Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-27 paper/main.tex
revise AD shortcomings & individual results

\todo[inline]{shorten the shortcoming; focus on ``opportunities'' for future research}

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal hints about
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room or locale (\texttt{groom})
to non-spatial hints.
% we did not choose se\_new and se\_old
We did not choose the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
The categories \texttt{se\_new} and \texttt{se\_old} were actually
heterogeneous: they rarely contained whole and thus a vague verbal descriptions
of landscapes (e.g. ``in a football stadium'', ``Forrest is running through the
jungle'') but mostly landmarks or buildings, and also non-spatial hints (e.g.
``Jenny as a teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of holistic but vague verbal descriptions of
landscapes correlate with differential hemodynamic activity in the PPA compared
to more concrete spatial hints.
% future studies
Hence, future studies might investigate if a homogeneous category of wholistic
but vague verbal descriptions (e.g. ``a mountain landscape'') compared to a
homogeneous categories of more specific verbal descriptions of landmarks (e.g.
``a beacon'') or houses (e.g. ``farmhouse'', ``apartment building'') lead to
different levels of hemodynamic activity.

@@

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}
%
Based on the fact that the annotation of speech still offered a more precise way
to operationalize the perception of spatial information then the annotation of
cuts and locations, we also hypothesized that data from the audio-description
could reveal the location of the PPA in individual persons.
%
To test if a auditory narrative could [in principle] substitute a visual
localizer experiment, we examined the individual results from the
audio-description's primary contrast.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
% in the current study
The audio-description's primary contrast yielded significant bilateral clusters
in 9 of 14 subjects (of which sub-04 shows just right-lateralized PPA ROI) and a
unilateral significant cluster in one subject.
% one threshold (and contrast) to rule them all
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting
$z$-threshold in a subject's unthresholded $z$-map by visual judgment, we used a
``one threshold fits all approach`` (Z>3.4, p<.05 cluster-corrected).
% group vs individual
Results on an individual level reveal that significant cluster are located in
the anterior part of individual PPA ROIs. Thus, the pattern that was revealed on
the group level is not just a by-product of the averaging process but can
reliably be found in individual study participants.
% conclusion
Lastly, our exploratory analyses suggest that a naturalistic auditory stimulus
is in principle suitable to localize (the anterior part) of a higher-level
visual area in the majority of subjects.
% chose the best contrast in the future
Similarly to \citep{sengupta2016extension} that chose the ``best'' of three
alternative contrasts (strict, relaxed, or simple contrast), future studies that
aim for individual diagnostics / ROI localization should also test more than one
contrast to gain the ``best'' individual ROIs.\todo{``best'' sounds pretty
shitty}

\todo[inline]{probably not really important but: what do results suggest
regarding individual differences?  Differences in alertness, attention to
spatial information, predisposition?  ``capability'' to process auditory spatial
information?}

@@

\todo[inlince]{concluding statement: essentially "natural stimuli, fuck yeah!;
re-use of existent data; using [and extending] an already existing annotation
for to operationalize a specific perceptual process}

@@

\todo[inline]{make this short; as expected almost everywhere null results ->

>>>>

\todo[inline]{at the moment positioned here; makes sense at a couple of other
positions; not shure yet}

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% we did not choose se\_new and se\_old
In the current study we did not include the categories that contained switches
from one setting to another (\texttt{se\_new} and \texttt{se\_old}) which one
might assume to contain the auditory equivalent to the ``optimal'' visual
stimulus type in the primary contrast.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[in a] football stadium'', ``[Forrest is running through
the] jungle'') but mostly landmarks or buildings and also non-spatial hints
(e.g. ``[Jenny as a] teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if holistic but also vague verbal descriptions of landscapes lead to
a different hemodynamic activity level than more concrete descriptions of a
landscape's content (e.g.``[a] beacon'', [a] ``farmhouse'', ``[an] apartment
building'').

@@

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}
%
Based on the fact that the annotation of nouns still offered a more precise way
to operationalize the perception of spatial information than the annotation of
cuts and locations, we also hypothesized that analyzing the data from the
audio-description could localize the PPA in individual persons.
%
Hence to test if an auditory narrative could [in principle] substitute a visual
localizer experiment, we examined the results from the audio-description's
primary contrast on an individual level.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$z$-threshold in an unthresholded $z$-map from one of three contrasts by visual
judgment, we used a ``one threshold fits all approach`` (Z>3.4, p<.05
cluster-corrected).
% in the current study
The audio-description's primary contrast that we used for all subjects yielded
significant bilateral clusters in 9 of 14 subjects (of which sub-04 shows only a
right-lateralized PPA ROI), and a unilateral significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
reveal that clusters are spatially restricted to the anterior part of individual
PPAs.
% conclusion
Thus, the increased hemodynamic activity in the anterior part of the PPA
revealed on the group level is not just a by-product of the averaging process
[as it can reliably be found in individual study participants.]
% conclusion
Lastly, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of an higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Further studies that aim for individual diagnostics / ROI localization should
nevertheless test more than one contrast to gain the ``best'' individual
ROIs.\todo{..ouff}

\todo[inline]{probably not important but: what do results suggest
regarding individual differences?  Differences in alertness, attention to
spatial information, predisposition?  ``capability'' to process auditory spatial
information?}

@@

\todo[inline]{concluding statement: essentially "natural stimuli, fuck yeah!;
re-use of existent data; using [and extending] an already existing annotation
for to operationalize a specific perceptual process}

@@

\todo[inline]{make this short; as expected almost everywhere null results ->
natural stimuli = suitable}
